\textbf{ Normalized Gaussian Processes }

### 2020-11-24 tex/ms.tex
better

    \mathbb{E}\big[ \tilde{\mathbf{x}} \tilde{\mathbf{x}}^\top \big]
    - \tilde{\pmb{\mu}}\tilde{\pmb{\mu}}^\top

@@

    \mathbb{E}\left[ \frac{\mathbf{x}\mathbf{x}^\top}{\bar{x}^2} \right]
    - \mathbf{J}_K

@@

    - \mathbf{J}_K

@@

    \mu + \frac{1}{K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}
Plugging this in and dividing the numerator and denominator in the expecation
by $\mu^2$, we obtain
            \left(1 + \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2
    - \mathbf{J}_K
            \mu^2 \mathbf{J}_K
            \mu \, \mathbf{j}_K\mathbf{u}^\top \mathbf{L}^\top
            \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
            \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top
            \left(1 + \frac{1}{\mu K}\mathbf{j}^\top \mathbf{L} \, \mathbf{u}\right)^2
    - \mathbf{J}_K
The denominator in the expression above makes direct evaluation of the expectation
$\big| \frac{1}{\mu K}\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u} \big| < 1$, we
can Taylor expand the covariance as
    \label{eq:SigmaTildeExp}
        \Bigg(
        \mu^2 \mathbf{J}_K
        \mu \, \mathbf{j}_K\mathbf{u}^\top \mathbf{L}^\top
        \mu \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
        \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top
        \Bigg)
        (-1)^n (n + 1) z^n
    - \mathbf{J}_K

@@

where we define the scalar quantity

@@

In the Appendix, we show that this expression may be written as
the infinite series

@@

@@

    \frac{1}{\mu^2} \pmb{\Sigma}

@@

    \sum\limits_{n=1}^\infty
    \frac{(-1)^n(n + 1)}{\mu^{n + 2}}

@@

    \pmb{\Lambda}_n

@@

    \pmb{\Lambda}_n

@@

    g_n \, \bar{\Sigma}^\frac{n}{2} \, (\pmb{\Sigma} + \mu^2\mathbf{J}_K)
    \, +
    K g_{n+1} \mu  \,
    \mathbf{S}^\frac{n + 1}{2}
    {\mathbf{S}^\top}^\frac{n + 1}{2}
    \, +
    n g_n \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma}

@@

where $\bar{\Sigma}$ is the average of all the elements in $\pmb{\Sigma}$ and

@@

@@

    \pmb{E}\big[|z|\big] < 1

@@

    \pmb{E}\big[z^2\big] &< 1

@@

    \frac{\bar{\Sigma}}{\mu^2} &< 1

@@

>>>>

    \mathbb{E}\big[ (\tilde{\mathbf{x}} - \tilde{\pmb{\mu}}) (\tilde{\mathbf{x}} - \tilde{\pmb{\mu}} )^\top \big]

@@

        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}_K\right)
        \left(\frac{\mathbf{x}}{\bar{x}} - \mathbf{j}_K\right)^\top
        \frac{\mathbf{x}\mathbf{x}^\top}{\bar{x}^2}
        -
        \frac{\mathbf{x}\,\mathbf{j}_K^\top}{\bar{x}}
        -
        \frac{\mathbf{j}\,\mathbf{x}_K^\top}{\bar{x}}
        \frac{\mathbf{x}\mathbf{x}^\top}{\bar{x}^2}
    -
        \frac{\mathbf{x}\,\mathbf{j}_K^\top}{\bar{x}}
    -
        \frac{\mathbf{j}_K\,\mathbf{x}^\top}{\bar{x}}

@@

    -
            (\pmb{\mu} + \mathbf{L} \mathbf{u})\mathbf{j}_K^\top
            \bar{x}
    -
            \mathbf{j}_K(\pmb{\mu} + \mathbf{L} \mathbf{u})^\top
            \bar{x}

@@

    \mu + \frac{1}{K}\mathbf{j}_K^\top \mathbf{L} \, \mathbf{u}
            & = \mu(1 + z)

@@

where we define the quantity

@@

Plugging this in and rearranging, we obtain

@@

    \label{eq:SigmaPQR}

@@

    \mathbf{P}
    -
    \frac{1}{\mu}
    \mathbf{Q}

@@

    \mathbf{Q}^\top
    \mathbf{R}
where we define the matrices
    \label{eq:Pexact}
    \mathbf{P} & \equiv
    \mathbb{E}\Big[
        \frac{z^2 \, \mathbf{J}_K}{(1 + z)^2}
        \Big]
    \\[0.5em]
    \label{eq:Qexact}
    \mathbf{Q} & \equiv
        \frac{z\, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top}{(1 + z)^2}
    \\[0.5em]
    \label{eq:Rexact}
    \mathbf{R} & \equiv
        \frac{ \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \, \mathbf{L}^\top}{(1 + z)^2}
The denominator in the expressions above makes direct evaluation of the expectations
$\big|z| < 1$, we can Taylor expand the matrices as
    \mathbf{P}
    (-1)^n (n + 1)

@@

        z^{n + 2}
    \\[0.5em]
    \mathbf{Q}
    (-1)^n (n + 1)
        z^{n + 1} \,
        \mathbf{L}
        \mathbf{u}
        \mathbf{j}_K^\top
    \\[0.5em]
    \mathbf{R}
    (-1)^n (n + 1)
        z^n \, \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top
In the Appendix, we show that these may be computed from
        z^{n + 2} \, \mathbf{J}_K
    (n + 1) g_{n} \, \bar{\Sigma}^\frac{n+2}{2} \, \mathbf{J}_K
    \\[0.5em]
        z^{n + 1} \, \mathbf{L} \, \mathbf{u} \, \mathbf{j}_K^\top
    (n + 1) K \, g_{n} \, \mathbf{S}^\frac{n+2}{2}
    \\[0.5em]
        z^n \, \mathbf{L} \, \mathbf{u} \, \mathbf{u}^\top \mathbf{L}^\top
    n \, g_{n} \, \mathbf{S}^\frac{n}{2}\pmb{\Sigma} + g_{n} \, \bar{\Sigma}^\frac{n}{2} \pmb{\Sigma}

@@

@@

@@

and $\bar{\Sigma}$ is the average of all the elements in $\pmb{\Sigma}$.
Inserting these expressions into Equation~(\ref{eq:SigmaPQR}), we obtain

@@

    \resizebox{.85\hsize}{!}{$
            (-1)^n (n + 1)^2 g_n
            \bar{\Sigma}^\frac{n+2}{2} \mathbf{J}_K
            -
            \frac{K}{\mu}\left( \mathbf{S}^\frac{n+2}{2} + {\mathbf{S}^\top}^\frac{n+2}{2} \right)
            \frac{n}{(n+1)\mu^2}
            \mathbf{S}^\frac{n}{2} \mathbf{\Sigma}
            \bar{\Sigma}^\frac{n}{2} \mathbf{I}_K
            \mathbf{\Sigma}
        $}

@@

    \mathbb{E}\big[|z|\big] < 1

@@

    \mathbb{E}\big[z^2\big]    & < 1

@@

    \frac{\bar{\Sigma}}{\mu^2} & < 1

@@

\xxx{THIS ALL NEEDS TO BE REWRITTEN!}
